Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-17 Paperfolder/Paperfolder.tex
updated versions sent to coauthors

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Public Health, Aichi Medical University
School of Medicine, Nagakute, Japan; \\
$^{2}$ \quad Departmet of Public Health, Fujita Health University School
of Medicine, Toyoake, Japan; \\
$^{3}$ \quad Public Health, Department of Social Medicine, Osaka
University Graduate School of Medicine, Osaka, Japan; \\
$^{4}$ \quad Department of Public Health, Faculty of Medicine, Hokkaido
University, Sapporo, Japan; \\
}
% Contact information of the corresponding author
\corres{Correspondence: Email.:
\href{mailto:chaochen@wangcc.me}{\nolinkurl{chaochen@wangcc.me}}; Tel.:
+81-561-62-3311. Department of Public Health, Aichi Medical University
School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan
(C.W.)}

>>>>

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Public Health, Aichi Medical University
School of Medicine, Nagakute, Japan; \\
$^{2}$ \quad Departmet of Public Health, Fujita Health University School
of Medicine, Toyoake, Japan; \\
$^{3}$ \quad Public Health, Department of Social Medicine, Osaka
University Graduate School of Medicine, Osaka, Japan; \\
$^{4}$ \quad Department of Public Health, Hokkaido University, Graduate
School of Medicine, Sapporo, Japan; \\
}
% Contact information of the corresponding author
\corres{Correspondence: Email.:
\href{mailto:chaochen@wangcc.me}{\nolinkurl{chaochen@wangcc.me}}; Tel.:
+81-561-62-3311. Department of Public Health, Aichi Medical University
School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan
(C.W.)}
